Bandwidth-Aware Reconfigurable Memory Design with Hybrid Memory Technologies

### 2011-04-04 paper.tex

\noindent{}{\bf{STT-RAM}} STT-RAM uses the magnetic property of the material and
uses Magnetic Tunnel Junction (MTJ) as its binary storage. As shown in
Fig.~\ref{fig:mram_cell}, MTJ contains two ferromagnetic layers and one tunnel
barrier layer. The direction of one ferromagnetic layer is fixed, which is
called the reference layer, while the direction of the other one can be changed
by passing a driving current, which is called the free layer. The relative
magnetization direction of two ferromagnetic layers determines the resistance of
MTJ. If two ferromagnetic layers have the same directions, the resistance of MTJ
is low, indicating a ``0'' state; if two layers have different directions, the
resistance of MTJ is high, indicating a ``1'' state.

@@

\noindent{}{\bf{RRAM}}

@@

Memristor, a portmanteau of ``memory resistor'', is a generalized resistance
that maintains a functional relationship between the time integrals of current
and voltage. Memristor was first theoretically predicted by Chua in
1971~\cite{memristor:chua} as the fourth fundamental circuit element from the
completeness of relations between the four basic circuit variables, namely,
current, voltage, charge, and flux-linkage. The first memristor practical
demonstration was presented by Williams \emph{et al.} in
2008~\cite{memristor:missing}. Fig.~\ref{fig:memristor} shows a conceptual view
of the memristor structure~\cite{memristor:missing}. The top electrode and
bottom electrode are two metal nanowires on platinum, and the thin titanium
dioxide film is sandwiched by the electrodes.

@@

>>>>

\noindent{}{\bf{STT-RAM}} STT-RAM uses the magnetic property of the material and
uses Magnetic Tunnel Junction (MTJ) as its binary storage. As shown in
Fig.~\ref{fig:mram_cell}, MTJ contains two ferromagnetic layers and one tunnel
barrier layer. The direction of one ferromagnetic layer is fixed, which is
called the reference layer, while the direction of the other one can be changed
by passing a driving current, which is called the free layer. The relative
magnetization direction of two ferromagnetic layers determines the resistance of
MTJ. If two ferromagnetic layers have the same directions, the resistance of MTJ
is low, indicating a ``0'' state; if two layers have different directions, the
resistance of MTJ is high, indicating a ``1'' state. \vspace{0.1in}

@@

\noindent{}{\bf{RRAM}} Memristor, a portmanteau of ``memory resistor'', is a
generalized resistance that maintains a functional relationship between the time
integrals of current and voltage. Memristor was first theoretically predicted by
Chua in 1971~\cite{memristor:chua} as the fourth fundamental circuit element
from the completeness of relations between the four basic circuit variables,
namely, current, voltage, charge, and flux-linkage. The first memristor
practical demonstration was presented by Williams \emph{et al.} in
2008~\cite{memristor:missing}. Fig.~\ref{fig:memristor} shows a conceptual view
of the memristor structure~\cite{memristor:missing}. The top electrode and
bottom electrode are two metal nanowires on platinum, and the thin titanium
dioxide film is sandwiched by the electrodes.

@@

\noindent{}{\bf{eDRAM??}}

@@

\subsection{Memory Hierarchy Design}

\subsection{Reconfiguration}

\subsection{Workload Behavior Prediction}
